### 2022-07-24 paper/akweury/document.tex
update an2 (Trignet)

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{tikz}
\usepackage{tikz-network}
\usetikzlibrary{calc,patterns,angles,quotes}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{rotating}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}
\subimport{./layers/}{init}
\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}

@@

The performance of neighbor based method is good enough for a well chosen $ k $, and it can be further improved by simply use different $ k $ for different area prediction. However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor selection and also reduce the number of possible neighbors of each point for a fixed $ k $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
	\label{fig:svd-noise}
	\caption{Evaluation of neighbor based method on a noised dragon model}
\end{figure}

% ---------------------- gated convolution neural network ------------------------
\section{Gated Convolution neural network for surface normal estimation}
\label{gcnn}

@@

Instead of using pooling layers for down/up samplings, gated convolution layer with stride $ (1,1) $ is used. The gated convolution using Sigmoid function for gating layer and LeakyReLU function for feature layer. All the layers are gated convolution layer with the exception of last two layers, which instead uses standard convolution layer to scale the output in range $\left[-1, 1\right]$. Other than the last two layers which use $ 1\times 1 $ kernels, all the gated convolution layer use $ 3\times 3 $ kernels with $ 1\times1 $ padding.

The input is 3D vertex with size $ 512\times512\times3 $, and output is $ 512\times512\times3 $ normal map, which has the same resolution. There are 3 times downsamplings, each scale with 3 gated convolution layers, the third layer has stride 2. The upsampling part interpolate the feature maps 3 times with 1 gated convolution layer in each scale.

It keeps the skip connection in UNet to remain the fine detail features.

% GCNN Architecture
\begin{figure}[!h]
	\centering
	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
	\begin{tikzpicture}
		%% -------------------------------------- parameters ------------------------------------------------
		\pgfmathsetmacro{\vdist}{0.4}

		\pgfmathsetmacro{\boxsizea}{3}	%% width 512
		\pgfmathsetmacro{\boxsizeb}{1.5}	%% width 256
		\pgfmathsetmacro{\boxsizec}{1}	%% width 128
		\pgfmathsetmacro{\boxsized}{0.7}	%% width 64

		\pgfmathsetmacro{\boxwidthd}{0.1}	%% width 1
		\pgfmathsetmacro{\boxwidtha}{0.2}	%% width 3
		\pgfmathsetmacro{\boxwidthb}{\boxwidtha*1.3}	%% width 32
		\pgfmathsetmacro{\boxwidthc}{\boxwidtha*3}		%% width 64

		\pgfmathsetmacro{\convwshift}{9}
		\pgfmathsetmacro{\preprocessingshift}{4}
		\pgfmathsetmacro{\labelshift}{1.5}
		\pgfmathsetmacro{\gconvwshift}{0}

		\pgfmathsetmacro{\secrowshift}{-6}

		\pgfmathsetmacro{\convrowstart}{4}
		\pgfmathsetmacro{\secondrowstart}{4}

		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
		\definecolor{gconvcolor}{rgb}{0.5,0.7,0.7}
		\definecolor{convcolor}{rgb}{0.5,0.7,0.3}
		\definecolor{gconvdilatedcolor}{rgb}{0.6,0,0.3}

		%% ---------------------------------- preprocessing --------------------------------------------
		%%  img_in 1x512x512
		\pgfmathsetmacro{\disttimes}{3.5}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-input.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {3D Vertex};

		\draw [-stealth](1.45,\yschift-1.8) -- (1.45,\yschift-2.6);

		\draw [-stealth]  (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);

		\pgfmathsetmacro{\disttimes}{10}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-depth-noise}};
		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {Add Noise};

		\draw [-stealth] (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);

		\pgfmathsetmacro{\disttimes}{16.5}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-depth.png}};
		\node[text width=2cm] at (\vdist*\disttimes+0.2,\yschift-1.5) {Depth Map};

		%% ----------------------------------- output normal map -------------------------------------
		\pgfmathsetmacro{\disttimes}{25}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-normal-gt.png}};
		\node[text width=2.5cm] at (\vdist*\disttimes,\yschift-1.5) {Normal Map};

		\draw [-stealth] (\vdist*\disttimes+0.2,\yschift-2.7) -- (\vdist*\disttimes+0.2,\yschift-1.8);

		%% ------------------------------------------- vertex input ----------------------------------------------
		%% 	d_in							3x512x512
		%%	dconv1: 	d_in-->x1 			32x512x512
		\pgfmathsetmacro{\disttimes}{1}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%%	dconv2:		x1-->x1				32x512x512
		\pgfmathsetmacro{\disttimes}{2}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%%	dconv3:		x1-->x1				32x512x512
		\pgfmathsetmacro{\disttimes}{3}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\draw (\vdist*\disttimes-0.2,\yschift-3.2) -- (\vdist*\disttimes-0.2,\yschift-4);
		\draw (\vdist*\disttimes-0.2,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-4);
		\draw [-stealth] (\vdist*\disttimes+6.5,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-3.2);

		%% downsample 1
		%%	dconv4:		x1-->x2				32x256x256
		\pgfmathsetmacro{\disttimes}{4}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv2:		x2-->x2				32x256x256
		\pgfmathsetmacro{\disttimes}{5}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv3:		x2-->x2				32x256x256
		\pgfmathsetmacro{\disttimes}{6}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\draw (\vdist*\disttimes-0.1,\yschift-1.6) -- (\vdist*\disttimes-0.1,\yschift-2.7);
		\draw (\vdist*\disttimes-0.1,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-2.7);
		\draw [-stealth] (\vdist*\disttimes+4.2,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-1.7);

		%% downsample 2
		%%	dconv4:		x2-->x3				32x128x128
		\pgfmathsetmacro{\disttimes}{7}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv2:		x3-->x3				32x128x128
		\pgfmathsetmacro{\disttimes}{8}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv3:		x3-->x3				32x128x128
		\pgfmathsetmacro{\disttimes}{9}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\draw (\vdist*\disttimes-0.1,\yschift-1.2) -- (\vdist*\disttimes-0.1,\yschift-1.8);
		\draw (\vdist*\disttimes-0.1,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.8);
		\draw [-stealth] (\vdist*\disttimes+1.8,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.2);

		%% downsample 3
		%%	dconv4:		x3-->x4				32x64x64
		\pgfmathsetmacro{\disttimes}{10}
		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-1}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv2:		x4-->x4				32x64x64
		\pgfmathsetmacro{\disttimes}{11}
		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv3:		x4-->x4				32x64x64
		\pgfmathsetmacro{\disttimes}{12}
		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%		%% dilated
		%		%%	dilated1:	x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{13}
		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%		%%	dilated2:	x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{14}
		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%		%%	dilated3:	x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{15}
		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%		%%	dilated4:	x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{16}
		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%		
		%		
		%		
		%		
		%		%%	dconv2:		x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{17}
		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%		%%	dconv3:		x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{18}
		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%% ----------------------------------- upsampling -------------------------------------

		%% upsample 1
		%% interpolate	x4-->x3_us			64x128x128
		\pgfmathsetmacro{\disttimes}{13}
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%% concatenate x3_us
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%% uconv1		x3_us-->x3			32x128x128
		\pgfmathsetmacro{\disttimes}{15}
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

>>>>

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{tikz}
\usepackage{tikz-network}
\usetikzlibrary{calc,patterns,angles,quotes}
\usepackage{breqn}
\usepackage{bm}
\usepackage{float}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{rotating}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}
\subimport{./layers/}{init}
\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}

@@

The performance of neighbor based method is good enough for a well chosen $ k $. However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
	\label{fig:svd-noise}
	\caption{Evaluation of neighbor based method on a noised dragon model}
\end{figure}

% ---------------------- gated convolution neural network ------------------------

\section{Photometric Stereo}
Photometric stereo was initially introduced by \cite{photometric-stereo}, which estimates the surface normal of the object by observing the object in the same position but under different illuminated scenes. It based on the fact that the light reflected by a surface is dependent on the surface normal and the light direction.

\subsection{Approaches}
Given an image $ I $, it can be decomposed in to two parts, the reflectance $ R $ and the shading $ S $,
\[ I = R\oplus S\]
where $ \oplus $ denotes the element-wise product. This decomposition of the image is based on the intrinsic image model, which proposed by  \cite{intrinsic-image}. It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
%% insert a image for decompositions
\begin{figure}[th]
	\centering
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
	\label{fig:intrinsic-image}
\end{figure}

In another word, the surface normal including the albedo can be obtained directly based on a set of images and light directions.

\section{Gated Convolution neural network for surface normal estimation}
\label{sec:gcnn}

@@

\begin{sidewaysfigure}[th]
	\centering
	\includegraphics[width=1\textwidth]{Figures/gcnn}
	\caption{The architecture of Gated convolution neural network (GCNN) based on Gated convolution and UNet Architecture.}
	\label{fig:gcnn-archi}
\end{sidewaysfigure}
In order to describe the network in a common way, the parameters of the network are represented by letters.
The network is constructed by a downsampling part and a upsampling part. In the downsampling part, the input is the $ X \in \mathbb{R}^{w\times w\times ch}$. The input matrix goes through 3 downsampling layer blocks, each block has two gated convolution layers with stride (1,1) and an extra gated convolution layers with stride (2,2) as a downsampling operation. 
The total three times downsamplings extract the geometry features $ X_v $ from input matrix $ X $ (represented as a regression function $ f $)
\[ f: X \rightarrow X_f \]
After the feature extraction, the network upsampling the feature map 3 times to get the output matrix $ Y $. Each upsampling consists of an interpolation operation uses nearest neighboring interpolations for resolution upsamling, then a concatenate layer that concatenate the interpolated result and the corresponding high resolution feature map  $ X_{df_1, df_2, ...} $  from the downsampling part. This is also called skip connection. In the last, a gated convolution layer is utilized to reduce the channel size to fit the next upsampling block. After the three times upsampling, two standard convolution layer is added in the last without activation function to predict the surface normal. The whole upsampling branch can be represented as a regression function $ n $,
\[ n: X_v, X_{df_1, df_2, ...} \rightarrow N \]
All the convolution layers in the network use same kernel size $ 3\times 3 $.

One of the key feature of the network is the output has the same size as the input. This is achieved by the (1,1) padding and the same channel number in the convolution layers. Thus the surface normal can be achieved 1-1 estimation. Another key point of the network is the robustness of the noise. The network takes semi-dense matrix as input then predicts the fully-dense matrix as output. The last feature is the multi-purpose using scenarios. In the description, no specific input type has been indicated. In this thesis, two application scenarios have been verified. The first is the missing-pixel estimation but with out the transformation of the style of the input matrix, which takes the semi-dense matrix as input and simply fill the missing pixels in the output. The second is the missing pixel estimation with style-transferred of the matrix. In this case, the network takes the semi-dense matrix as input, the output matrix is fully-dense but each pixel has the different meaning as the input. Actually, the first scenario can be consider as the specially case of the second scenario which the style of output and the input remain the same. The network is test in Chapter \ref{ch:05}, which is shown the good performance on noise filtering task and also the normal surface estimation task.
